\documentclass{fheadnote}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{url}
\usepackage{verbatim}
\usepackage{textcomp}
\usepackage{footnote}
\usepackage{hyperref}

\begin{document}

\begin{titlepage}

   \fheadreport{2012/001}
   \date{\today}

   \title{CMS VBF Mini Workshop}

   \begin{Authlist}
      Yi Chen
      \Instfoot{Institute}{California Institute of Technology}
   \end{Authlist}

   % \collaboration{FHead collaboration}

   \begin{abstract}
      CMS VBF mini workshop notes on Aug. 30, 2012.
   \end{abstract}

\end{titlepage}

\setcounter{page}{2}

\section{Notes from talks}

\subsection{P. Harris, VBF overview}

\begin{enumerate}
\item 30 fb$^{-1}$ expect roughly 72/36 events.
\item Important variables: $\Delta \eta_{jj}$, $m_{jj}$
\item $\Delta \phi$ between jets tells us about CP-even vs. SM vs. CP-odd
\item ggH + 2 jets: jets are mostly gluon-jets
\item ggH + 2 jets looks like background in the important variables.
\item Treatment of uncertainty on central jet veto is divergent.
\item Maybe we can look at Madgraph-generated H+jj H+jjj samples to get an idea
\item Si pointed out that $p_T$ cut is important.  20 GeV is too low for example.
   If too low we start to be sensitive to various things
\item Si: Madgraph didn't include loop diagrams, so systematics studies might not be covering.
   Maybe use MC@NLO.
   Emanuele: The reason that we didn't use MC@NLO in the past two years is that the DY is not well-described.
\item PU jet rejection, forward jet JES
\end{enumerate}

\subsection{P. Musella, $H^0 \rightarrow \gamma\gamma$}

\begin{enumerate}
\item For pileup rejection, MVA trained on Z+jet is sub-optimal.  Under investigation.
\item No central jet veto.
\item Showed efficiency curve for variables alone.  In reality they used two variables (RMX, beta star),
   but combined curve not shown.   Christoph don't understand.
\item Different approaches to improve VBF tagging:  MVA, $M_{jj}$ + $M_{\gamma\gamma}$ fit, di-photon MVA + $M_{\gamma\gamma}$ fit.  Typical improvement is 10-20\%.
\item MVA VBF tag.  They used 2 jets above 20 GeV.  Quoted improvement is 20\%.
   Markus argued that this will affect result.
   Pasquale argued that it doesn't matter much.
\item Expected gain in coupling measurement sensitivity is about 10\%.
\item 2D fit.  Caveat: measuring mass distribution and extrapolate from low MVA to large MVA.
\item gg contamination uncertainty large.  Estimated by comparing different {\sc pythia} tunes.
   Markus questions whether this is a good idea to do it this way.
   Emanuele: we can't really justify the coverage of this method.
   Someone over evo: we did this 20 years ago.
   Christoph: we need to use the one that makes more sense, even if it's still not ideal.  We need to have some conherence too.
\item Ideas to reduce gg uncertainty.  Improve simulation, reduce contamination, data-driven (from $M_{jj}$ shape for example).
\end{enumerate}

\subsection{L. Quertenmont, $H^0 \rightarrow Z^0Z^0$}

\begin{enumerate}
\item Sorry, I was distracted...
\end{enumerate}

\subsection{A. Massironi, $H^0 \rightarrow W^+W^-$}

\begin{enumerate}
\item In the lvjj, require 4 jets.  2 with largest delta eta are the tag jets.  Then cut on delta eta and
   Mjj of the tagged jets.  Markus questioned that the Mjj cut might kill everything.
\item Large uncertainty on gg contamination again.  gg contamination level is about 15\% here
\item Top background (di-lepton channel) estimated using b-tag efficiency
\end{enumerate}

\subsection{M. Chan, $H^0 \rightarrow \tau\tau$}

\begin{enumerate}
\item For the semi-hadronic channels, train BDT using muon channel.  For e-mu channel, train separately.
\item For BDT input, included variables like delta phi jj ==> CP measurement will be more complicated.
\item Showering uncertainty is taken from WW directly.
\end{enumerate}

\subsection{S. Bansal, $H^0 \rightarrow bb$}

\begin{enumerate}
\item Using q-g separation.  Collect variables and throw into TMVA
\item Jet PT regression to improve resolution
\end{enumerate}

\subsection{Final remarks}

\begin{enumerate}
\item We rely heavily on MC.  Maybe we can try different generators, etc.
\item Everyone is tired and doesn't talk too much.
\item Showering uncertainty is a sticky point.  Christoph pointed out that there's a note from Phil.
\end{enumerate}


\pagebreak

\end{document}
